\pdftitle

### 2017-05-17 maxNt.tex
discussion

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-18T01:18:11+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\begin{abstract}
  \mynote{Better title?}
  ***%  The abstract must be limited to one paragraph.
\end{abstract}

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-18T01:43:11+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\begin{abstract}
  This note has three nested purposes. The first purpose is to show that
  the \me\ method can be applied to a representative random sample of a
  population, to generate its probability distribution, along two different
  routes. Both routes appear legitimate, but they give inequivalent
  results. Which route should be chosen? Some arguments are presented in
  favour of one. The second more general purpose, motivated by the above
  dilemma, is to remind readers that models like \me\ may contain hidden
  assumptions; in this case the hidden an unnatural assumption that the
  sample modelled is isolated from the rest of the population. The third
  purpose is to promote some old but possibly forgotten probability
  formulae that may be useful in neuroscientific sampling contexts.
  % The abstract must be limited to one paragraph.
\end{abstract}
